Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-06-10 analysis/paper/paper.Rmd
Update software ranking text

There were `r as.character(english(length(unique(rrpp_software$software_used))))` unique software applications recorded being used in the articles that were evaluated.
These included desktop programs, web-based software and databases.
From the top ten most frequently cited software, the most frequently cited program was `r tab_s[1, 1]`, where different versions were not distinguished for this work.
The next three programs were statistical software, SAS (`r scales::ordinal(which(tab_s == "SAS"))`), SPSS (`r scales::ordinal(which(tab_s == "SPSS"))`) and R (`r scales::ordinal(which(tab_s == "R"))`) with two other statistical programs also frequently cited, GenStat and Statistica (tied 8th).
The remainder of the top ten programs we found were related to sequence analysis, *i.e.*, Clustal (`r scales::ordinal(which(tab_s == "CLUSTAL"))`), BLAST (`r scales::ordinal(which(tab_s == "BLAST"))`), and BioEdit (`r scales::ordinal(which(tab_s == "BIOEDIT"))`) or phylogenetic analysis MrBayes (`r scales::ordinal(which(tab_s == "MRBAYES"))`).
The most general-purpose software cited in the top 10 was Excel® (`r scales::ordinal(which(tab_s == "EXCEL"))`).
The Python programming language was cited only twice.

>>>>

There were `r as.character(english(length(unique(rrpp_software$software_used))))` unique software applications recorded being used in the articles that were evaluated.
These included desktop programs, web-based software and databases.
From the top ten most frequently cited software, the most frequently cited program was `r tab_s[1, 1]`, where different versions were not distinguished for this work.
The next three programs were statistical software, SAS (`r scales::ordinal(which(tab_s == "SAS"))`), SPSS (`r scales::ordinal(which(tab_s == "SPSS"))`) and R (`r scales::ordinal(which(tab_s == "R"))`) with two other statistical programs also frequently cited, GenStat and Statistica (tied 8th).
The remainder of the top ten programs we found were mostly related to sequence analysis, *i.e.*, Clustal (`r scales::ordinal(which(tab_s == "CLUSTAL"))`), BLAST (`r scales::ordinal(which(tab_s == "BLAST"))`), and BioEdit (9th) or phylogenetic analysis MrBayes (8th), tied with the most general-purpose software cited in the top 10, Excel®.
In tenth place was FigTree, used for phylogenetic trees.
The Python programming language was cited only twice.
